% cv-us.tex
% $Id: cv-us.tex,v 1.32 2007/11/06 13:59:29 jrblevin Exp $
%
% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2007 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jrblevin.freeshell.org
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.
%
% Durham, February 17, 2007
%
%%---------------------------------------------------------------------------%
%
% Notes:
%
% * THIS IS IMPORTANT.
%   Don't forget to change `pdfauthor' and `keywords' in the \hypersetup
%   section below. Lots of other people's CVs show up in Google when I type my
%   name because they didn't change these and my name is in their PDF metadata.
%
% * To create a new page use: \newpage \opening
%
% * res.cls includes an \address{} command which can be used up to twice,
%   but my address is too long for the format it uses.
%
% * Alternate documentclass statement to put headings in margin:
%   \documentclass[margin,line,11pt,final]{res}
%
% * Can divide publication/presentation list into subsections by year:
%   \section{\bf\small\hspace{8mm}2006}
%
%%----------------------------------------------------------------------------%

\documentclass[overlapped,line,letterpaper]{res}
% \usepackage{simplemargins}
% \setleftmargin{1.5in}
% \setrightmargin{1.5in}



\usepackage{ifpdf}
\usepackage{helvetica}
\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi


\hypersetup{
  letterpaper,
  colorlinks,
  urlcolor=black,
  pdfpagemode=none,
  pdftitle={Curriculum Vitae},
  pdfauthor={J Justin Donaldson},
  pdfcreator={$ $Id: cv-us.tex,v 1.32 2007/11/06 13:59:29 jjdonald Exp $ $},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={network analysis interaction hci design music informatics information retrieval}
}

%%===========================================================================%%

\begin{document}


%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

% Make a nicer C++
\def\Cplusplus{C{\raise.5ex\hbox{\footnotesize ++ }}}

%---------------------------------------------------------------------------

\name{Justin Donaldson}

\begin{resume}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}  l  r  }
  3302 39th Ave W	& Phone: (919) 289-9553 \\
  Seattle, WA 98199	& {\tt jdonaldson@gmail.com} \\
			&  \\ {\tt \url{http://www.linkedin.com/in/jjustindonaldson}}        
\end{tabular*}

%---------------------------------------------------------------------------

\section{\bf Education}
Ph.D. Informatics, Indiana University, 2011 

M.S. Human-Computer Interaction, Indiana University, 2006

B.S. Computer Science, DePauw University, 2001

%---------------------------------------------------------------------------


\section{\bf Work Experience}

\title{Lead Developer}
\employer{Salesforce.com}
\location{Seattle, WA}
\dates{2013-}
\begin{position}
  Responsibilities included developing the first iteration of Search interfaces for the new Salesforce S1 platform, as well as developing the first efforts for a machine-learned search results ranking system.
\end{position}

\title{President, Co-founder}
\employer{BigML, Inc.}
\location{Corvallis, OR}
\dates{2011-2013}
\begin{position}
Responsibilities include early business development, general administration, and development of core front end features. Implemented web based framework and novel visualizations for machine learning systems on cloud-based infrastructures.
\end{position}


\title{Applied Research Manager}
\employer{Strands Labs, Inc.}
\location{Corvallis, OR}
\dates{2004-2011}
\begin{position}
Worked as chief developer of novel web related technologies related to recommender systems and rich internet applications with a focus on interactive visualizations.  Managing remote interns.  Co-hosting an international student summer programming project for the web language haXe \url{http://labs.strands.com/Summer2008HaxeProject/}.
\end{position}

\title{Independent Consultant}
\employer{Self Employed}
\location{Indianapolis, IN}
\dates{2001-2002}
\begin{position}
Worked for \href{http://www.hju.com}{H. J. Umbaugh \& Associates Certified Public Accountants}, and \href{http://www.dcmol.com}{Donaldson Capital Management, LLC}.
Developed large (at the time) database and form applications for monitoring and comparing utility (water/power/gas) costs among counties in the Midwest region.  Queries and comparisons were used for the purposes of establishing municipal bonds rates.  
Developed database and form applications for managing customer relationships. 

\end{position}

\section{\bf Research Experience}

\begin{format}
\title{l}\dates{r}\\
\employer{l}\location{r}\\
\body\\
\end{format}

\title{Research Assistant}
\title{Research Assistant}
\employer{Dr. Filippo Menczer and Dr. Javed Mostafa}
\location{Indiana University}
\dates{2002--2003}
\begin{position}
Worked as a research assistant for Dr. Menczer, developing a flexible multi-agent classifier system on the IU AVIDD high performance computing cluster.  This system investigated the trade offs between monolithic and agent based textual classifier performance in information retrieval systems.  
\end{position}

\employer{Dr. Erik Stolterman}
\location{Indiana University}
\dates{2003--2004}
\begin{position}
Worked as a research assistant for Dr. Stolterman, investigating the interaction of aesthetics with usability.  Conducted extensive literature review and developed a novel technique for identifying cultural trends in color and structural preferences for web pages.
\end{position}


\title{Research Intern}
\employer{MyStrands/MusicStrands}
\location{Corvallis, Oregon; Barcelona, Spain}
\dates{2005--2010}
\begin{position}
  Development of interactive visualization systems for personal recommendation retrieval, and global recommendation analysis.  Time-series analysis and applications of play streams.  Large scale network decomposition analysis and applications.  Long term visualization and analysis of mutual fund portfolios.
\end{position}

%---------------------------------------------------------------------------

\section{\bf Teaching Experience}

\begin{itemize}
\item Associate Instructor for Dr. Martin Siegel, HCI I\&II, Indiana University, Fall 2002 and Spring 2003 
\item Associate Instructor for Dr. Blevis, HCI Studio Class, Fall 2003
\end{itemize}

% \newpage
% \opening

\subsection{\bf Conference Papers}
Donaldson, J., and Hazlewood, W. 2008. Candidate Mapping: finding your place amongst the candidates. In \emph{IEEE Proceedings of the 12th International Conference on Information Visualisation} (London, U.K. July 07-11, 2008). IV '08. IEEE, Los Alamitos, CA, 63-68.

Donaldson, J. J., Conover, M., Markines, B., Roinestad, H., and Menczer, F. 2008. Visualizing social links in exploratory search. In \emph{Proceedings of the Nineteenth ACM Conference on Hypertext and Hypermedia} (Pittsburgh, PA, USA, June 19 - 21, 2008). HT '08. ACM, New York, NY, 213-218. \\ DOI= \url{http://doi.acm.org/10.1145/1379092.1379132} 

Lim, Y., Stolterman, E., Jung, H., and Donaldson, J. 2007. Interaction gestalt and the design of aesthetic interactions. In \emph{Proceedings of the 2007 Conference on Designing Pleasurable Products and interfaces} (Helsinki, Finland, August 22 - 25, 2007). DPPI '07. ACM, New York, NY, 239-254. 
DOI= \url{http://doi.acm.org/10.1145/1314161.1314183} 

Donaldson, J., Knopke, I., and Raphael, C. 2007. Chroma Palette: chromatic maps of sound as granular synthesis interface. In \emph{Proceedings of the 7th international Conference on New interfaces For Musical Expression} (New York, New York, June 06 - 10, 2007). NIME '07. ACM, New York, NY, 213-218. \\DOI= \url{http://doi.acm.org/10.1145/1279740.1279782} 

Baccigalupo, C., Donaldson, J., and Plaza, E. 2008. Uncovering Affinity of Artists to Multiple Genres from Social Behaviour Data.  In \emph{Proc. of 9th international Conference on Music Information Retrieval} (Philadelphia, PA, September 14 - 18, 2008). ISMIR '08.


\subsection{\bf Other Invited Papers (Articles/Workshops/Tutorials)}
Martin, F., Donaldson, J., Ashenfelter, A., Torrens, M., and Hangartner, R. The Big Promise of Recommender Systems. \emph{AI Magazine} Vol 32, Number 3. 2012.

Donaldson, J. and Lamere, P. 2009. Music Visualization for Discovery.  (Extended) Proc. of \emph{International Society for Music Information Retrieval}. Kobe, Japan 2009. October 26-30. (ISMIR '09) 

Donaldson, J.: Music recommendation mapping and interface based on structural network entropy. In: \emph{Oria, V., Elmagarmid, A., Lochovsky, F., Saygin, Y. (eds.) Proceedings of the 23rd International Conference on Data Engineering Workshops (WPRSIUI'07) }, ICDE '07. IEEE Computer Society, Los Alamitos, CA, 811-817. 

Donaldson, J. 2007. A hybrid social-acoustic recommendation system for popular music. In \emph{Proceedings of the 2007 ACM Conference on Recommender Systems} (Minneapolis, MN, USA, October 19 - 20, 2007). RecSys '07. ACM, New York, NY, 187-190.\\DOI= \url{http://doi.acm.org/10.1145/1297231.1297271}



\subsection{\bf Invited Student Design Competitions}
Donaldson, J., Genkina, A., MacArthur, S., Ozakca, M., and Stephano, A. 2004. DOVE: digital Olympic voting environment. In \emph{CHI '04 Extended Abstracts on Human Factors in Computing Systems} (Vienna, Austria, April 24 - 29, 2004). CHI '04. ACM, New York, NY, 1631-1635. \\DOI= \url{http://doi.acm.org/10.1145/985921.986176} 

Donaldson, J., Evnin, J., and Saxena, S. 2005. ECHOES: encouraging companionship, home organization, and entertainment in seniors. In \emph{CHI '05 Extended Abstracts on Human Factors in Computing Systems} (Portland, OR, USA, April 02 - 07, 2005). CHI '05. ACM, New York, NY, 2084-2088. \\DOI= \url{http://doi.acm.org/10.1145/1056808.1057104}



\subsection{\bf Posters}
Donaldson, J.: ZMDS: Visualizing Structural Entropy in Queried Network Sub-graphs.   In Proc. Of NetSci 2006. Available at: \url{http://vw.indiana.edu/netsci06/conference/Donaldson_ZMDS_.pdf}

Donaldson, J. 2006. Limestick: designing for performer-audience connection in laptop based computer music. In \emph{CHI `06 Extended Abstracts on Human Factors in Computing Systems} (Montr\'eal, Qu\'ebec, Canada, April 22 - 27, 2006). CHI `06. ACM, New York, NY, 712-717. \\ DOI= \url{http://doi.acm.org/10.1145/1125451.1125595} 



\subsection{\bf Book Chapters}
Lim, Y., Donaldson, J., Jung, H., Kunz, B., Royer, D., Ramalingam, S., Thirumaran, S., and Stolterman, E. 2007. Emotional Experience and Interaction Design. In Beale, Peter (Ed.), \emph{Affect and Emotion in Human-Computer Interaction}.

\subsection{\bf Patents}
Donaldson, Justin. Personal Music Recommendation Mapping. WIPO No. WO/2008/051882. 	 

Donaldson, Justin. Real-Time Visualization of User Consumption of Media Items. WIPO no. WO/2010/040082
%------------------------------------------------------------------------------

% \section{\bf Scientific Software}
% 
% Blevins, J., J. Heath, and W. Hereman (2002):
% \href{http://www.mines.edu/fs_home/whereman/software/PDESolutionTester/}
% {\texttt{PDESolutionTester}},
% A Mathematica program for the symbolic verification of exact solutions of
% nonlinear partial differential equations.

%------------------------------------------------------------------------------

% \section{\bf Presentations}
% 
% ``Solving Nonlinear Wave Equations with Mathematica,''
% North Carolina State University, April 23, 2003.

%---------------------------------------------------------------------------

\section{\bf Service}

\begin{itemize}
\item Reviewer/Organizer: International Joint Conference on Artificial Intelligence (IJCAI 11), Conference on Visualization and Data Analytics (VDA 09), International Conference on Music Information Retrieval (ISMIR 07 \& 10), Workshop on Music Recommendation and Discovery (WOMRAD 10), ACM Conference on Human Factors in Computing Systems (CHI 07), Recommenders Summer School 2006 (predecessor to RECSYS). 
\item President, Graduate Informatics Student Association, Indiana University,
  2003-2004
\end{itemize}

%%---------------------------------------------------------------------------%%

\section{\bf Honors and Awards}
\begin{itemize}
	\item Top Conference Poster Award – NetSci 2006:
	“ZMDS: Visualizing Structural Entropy in Queried Network Sub-graphs”
	\item International Student Design Competition Finalist, (4th Place) CHI 2004:
	“DOVE: Digital Olympic Voting Environment”
	\item MusicStrands/MyStrands/Strands Sponsored Researcher 2006-2010 
	\item DePauw Academic Merit Scholarship 
	1997-2001
	\item DePauw Math and Science Scholarship 
	1997-2001
	\item Travel Grants from NSF for IPAM SEWS Workshop, RECSYS `07, and IV `08

\end{itemize}

%%---------------------------------------------------------------------------%%
% \section{\bf Computer Skills}
% 
% \begin{itemize}
% \item Expert: \Cplusplus, Fortran, Stata, Perl, \LaTeX, Linux
% \item Intermediate: Matlab, SQL, Ruby, SAS, Mathematica
% \item Basic: Assembly, Java
% \end{itemize}

%%---------------------------------------------------------------------------%%

% I use RCS for revision control.  This part simply puts the revision
% information at the end. Comment this out if you don't use RCS or CVS.
% \begin{center}
% \vspace{\fill}\ \newline
% {\tiny \rm $ $RCSfile: cv-us.tex,v $ $ }
% {\tiny \rm $ $Date: 2007/11/06 13:59:29 $ $ }
% {\tiny \rm $ $Revision: 1.32 $ $ }
% \end{center}

\end{resume}

\end{document}

%%===========================================================================%%
